\documentclass[letterpaper,11pt]{article}

\usepackage[top=0.5in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{graphicx}

\hypersetup{colorlinks=false}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.4pt}
\fancyfoot[L]{\small\textbf{\textcolor[HTML]{003F8A}{UBC Science Co-op}}}
\fancyfoot[R]{\small science.coop@ubc.ca\ \textbar\ 604-822-9677}

% Section formatting
\titleformat{\section}{\bfseries\large}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

% No paragraph indent
\setlength{\parindent}{0pt}

% Compact lists
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=1.5em}

\begin{document}

% ---------- HEADER ----------
\begin{center}
    {\LARGE \textbf{Lester Cheng}} \\[4pt]
    (778) 302-0038 \quad | \quad \href{mailto:lestercheng3@gmail.com}{lestercheng3@gmail.com}
\end{center}

% ---------- TECHNICAL SKILLS ----------
\section*{TECHNICAL SKILLS}

\begin{tabular}{@{}p{3.5cm} l}
    \textbf{Programming}      & : Java, C, C++, Python, TypeScript/JavaScript \\
    \textbf{Tools/Environment} & : Visual Studio Code, IntelliJ, Git, GitHub, Figma, Supabase, Prisma \\
    \textbf{Web}              & : HTML, CSS, Next.js, Flask, React, Tailwind CSS \\
    \textbf{Databases}        & : PostgreSQL \\
\end{tabular}

% ---------- PROJECTS ----------
\section*{PROJECTS}

\noindent\textbf{Note-Taking App (Personal)} $|$ \textit{TypeScript, Next.js, React, Tailwind, PostgreSQL} \hfill Jan. 2026 -- Present
\begin{itemize}
    \item Built a full-stack notes application using Next.js App Router with server components and server actions, handling routing, data fetching, and business logic entirely on the server.
    \item Designed a relational PostgreSQL database schema with Prisma ORM and connection pooling, paired with Supabase Auth for end-to-end secure user data management.
    \item Integrated Gemini API to enable AI-powered note enhancements including auto-summarization and writing assistance, streamlining user workflows through automated suggestions.
\end{itemize}

\vspace{4pt}
\noindent\textbf{Stock Watchlist Web App (Personal)} $|$ \textit{Python, Flask, HTML, CSS} \hfill Nov. 2025 -- Dec. 2025
\begin{itemize}
    \item Built a full-stack stocks tracking app allowing users to search, add, and remove ticker symbols from a persistent watchlist.
    \item Integrated the yfinance API to dynamically fetch and render real-time market metrics, including current pricing, daily fluctuations, volume, and daily highs/lows.
    \item Designed a RESTful Flask backend utilizing GET/POST routing, session-based flash messaging, and lightweight JSON data persistence.
\end{itemize}

\vspace{4pt}
\noindent\textbf{Gamified Study Timer (Hackathon)} $|$ \textit{Figma, TypeScript, CSS, React} \hfill Nov. 2025
\begin{itemize}
    \item Worked in a team of four and developed the frontend UI of a productivity application based on the Pomodoro Technique that integrates timed study intervals with gamified break periods.
    \item Achieved a Top 3 overall placement at HackCamp 2025 by successfully designing, prototyping, and pitching the React interface.
\end{itemize}

% ---------- WORK EXPERIENCE ----------
\section*{WORK EXPERIENCE}

\noindent\textbf{Lab Support Technician} $|$ Canadian Food Inspection Agency \hfill Jan. 2023 -- Aug. 2023
\begin{itemize}
    \item Performed quality control tests, routine microbiological testing of food commodities, and assisted in the maintenance of quality assurance documents and procedures in the microbiology laboratory.
\end{itemize}

\vspace{4pt}
\noindent\textbf{Shift Leader} $|$ Carl's Jr. \hfill May 2018 -- April 2022
\begin{itemize}
    \item Managed high-volume shift operations for 100+ daily customers, consistently maintaining high service standards while overseeing cash audits, financial transactions, and store opening and closing protocols.
\end{itemize}

% ---------- EDUCATION ----------
\section*{EDUCATION}

\noindent\textbf{Bachelor of Computer Science (BCS), Year 3} \hfill Sep. 2025 -- Present \\
University of British Columbia, Vancouver, BC \\
Expected Graduation: May 2028

\vspace{4pt}
\noindent\textbf{Bachelor of Science, Honours Microbiology \& Immunology} \hfill Sep. 2020 -- May 2025 \\
University of British Columbia, Vancouver, BC

\end{document}
